mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-09 Draft2.Rmd
few comments

```{r, results="asis"}
t <- quote(omit_left(a + b))
mathout(t)

catmath(omit_left(a + b))
```

```{r, results="asis"}
t <- quote(omit_right(a + b))
mathout(t)

catmath(omit_right(a + b))
```

@@

```{r, results="asis"}
t <- quote(add_left(a + b))
mathout(t)

catmath(add_left(a + b))
```

```{r, results="asis"}
t <- quote(add_right(a + b))
mathout(t)

catmath(add_right(a + b))
```

@@

```{r, results="asis"}
t <- quote(add_right(a + b))
mathout(t)

catmath(add_right(a + b))
```

```{r, results="asis"}
t <- quote(instead(a, b) + c)
mathout(t)

catmath(instead(a, b) + c)
```

>>>>

In this first example the function highlights that the student forgot to add the left-hand side of the expression and it does that by striking the missing part. In this case the letter A and the operator `+`.
Similarly the function `omit_right` does the same for the omissions in the right-hand side of the expression. Finally the function `omit()` can be used, for instance, to highlight the omission in the elements of a list.

```{r, results="asis"}
t <- quote(omit_left(a + b))
mathout(t)
```

```{r, results="asis"}
t <- quote(omit_right(a + b))
mathout(t)
```

@@

The functions `add_left()`, `add_right()`, `add()` reported below follow the same way of reasoning, but they account for the mistakes made in adding incorrect elements in the expression. They highlight the redundant element placing it in a box.

```{r, results="asis"}
t <- quote(add_left(a + b))
mathout(t)
```

```{r, results="asis"}
t <- quote(add_right(a + b))
mathout(t)
```

@@

Finally the function `instead( , )` place a curly bracket under the incorrect element  and provides its correct version under the curly bracket. In order to provide the correction with this function one must fill it with its wrong and correct terms in this order: `instead(wrong, correct)`. An example of its use its provided below.

```{r, results="asis"}
t <- quote(instead(a, b) + c)
mathout(t)
```
